Benefits and risks of diversification\\ for individual fishers\\ Benefits of diversification and risks of changing strategies for individual fishers\\ Benefits of diversification are unavailable to many fishermen\\

### 2016-12-06 portfolio/text/anderson-etal-rev-pfx.tex
Rework introduction and start cleaning up paper
Create and add IFQ figure to supplement
Switch to a numbered citation system
Tweak knitting, title, and copyediting

\documentclass[12pt,english]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabu} % for spacing between rows in longtable
\usepackage{titlesec}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{commath} % for \abs{}

@@

\usepackage[round,sectionbib]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}

@@

\title{Benefits of diversification and risks of changing strategies for individual fishers\\
Benefits of diversification are unavailable to many fishermen\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson$^X$,
\ldots
}

\newlabel{tab:strategies}{1}
\newlabel{fig:fe}{1}
\newlabel{fig:re}{2}
\newlabel{fig:spoke-all}{3}
\newlabel{fig:resid}{4}
\newlabel{fig:resid-downside}{5}
\newlabel{fig:str-yrs}{6}

>>>>

\documentclass[12pt,english]{article}
\usepackage{geometry}
\geometry{verbose, letterpaper, tmargin = 2.54cm, bmargin = 2.54cm,
  lmargin = 2.54cm, rmargin = 2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabu} % for spacing between rows in longtable
\usepackage{titlesec}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{commath} % for \abs{}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{4pt}\setlength{\parskip}{0pt}}

@@

% \usepackage[round,sectionbib]{natbib}
% \bibpunct{(}{)}{;}{a}{}{;}

@@

\title{
  Benefits and risks of diversification\\ for individual fishers\\
  Benefits of diversification and risks of 
  changing strategies for individual fishers\\
Benefits of diversification are unavailable to many fishermen\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson$^X$,
\ldots
}

\newlabel{tab:strategies}{1}
\newlabel{fig:fe}{1}
\newlabel{fig:re}{2}
\newlabel{fig:spoke-all}{3}
\newlabel{fig:resid}{4}
\newlabel{fig:resid-downside}{5}
\newlabel{fig:str-yrs}{6}
\newlabel{fig:ifq}{7}
